Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
Replacing maaslin?

@@

```{r fit asine}
source("fit_asine.R")
source("taxa_names_functions.R")
```

>>>>

options(max.print=1000)

@@

```{r fit asine}
source("fit_asine.R")
source("taxa_names_functions.R")

options(max.print=1000)

pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
pseq.genus.core.comp <- microbiome::transform(pseq.genus.core, "compositional")

res <- lapply(c2l(var.BP), function(BP)
    fit_asine(pseq.genus.core.comp, variables = c(BP, var.CL)))

asine.df <- data.frame()

res.trim <- lapply(c2l(var.BP), function(BP)
    lapply(c2l(names(res[[BP]])), function(name) res[[BP]][[name]] %>%
                                                 tidy %>%
                                                 dplyr::filter(grepl(BP, term)) %>%
                                                 mutate(taxa = name)))

map_df(res.trim, ~do.call(rbind, .x)) %>%
    dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
    arrange(Qval)

maaslin <- do.call(rbind, lapply(c2l(var.BP), function(BP) res[[BP]]))
saveRDS(maaslin, file = "rds/maaslin.rds")
```

```{r quit}
quit()
```
